### 2018-05-30 1_intro.tex
Complete everything. Left only polishing.
Add Acknowledgments.

Most modern computer systems contain large parts that operate concurrently.
Although the parallelisation of a system can drastically improve its performance, it opens numerous of problems regarding correctness, robustness and reliability, which makes the concurrent program design one of the most difficult problems of programming~\cite{mckenney2017parallel}.
In this work, we consider only \textit{Symmetric Multiprocessor (SMP)} parallelism (systems with multiple processors connected to a single shared memory), leaving aside the discussion on distributed concurrency (systems with autonomous nodes that communicate with each other by passing messages through the network).
%Leaving aside questions on the performance improvement of the system parallelisation, we explore the questions of the \textit{memory consistency},
We are discussing mostly the questions on the \textit{memory consistency} rather than performance benefits of the concurrency as the inconsistent memory operations can create new program behaviours, unexpected from the programmer's point of view (as well as the loss of expected behaviours), which all can be considered as a security flaw.

@@

The very first tool that performs the WMM-aware portability analysis is \porthos{}%
%
\footnote{The \porthos{} project web site: \url{http://github.com/hernanponcedeleon/PORTHOS}} %
%
introduced in April~2017~\cite{Porthos17a}.
This tool reduces described problem to a bounded reachability problem, which can be solved via an SMT-solver (see Section~\ref{ch:enc:bmc}).
This approach allows to capture symbolically the semantics of analysing program and both weak memory models into a single SMT-formula, augmented by the reachability assertion.
As most modern SMT-solvers are efficient enough to be able to operate the state space of size millions of variables bounded by millions of constraints~(\cite{malik2009boolean}), the used method can be applicable in solving the real-world problems.
% about SAT: https://courses.cs.washington.edu/courses/csep573/11wi/lectures/ashish-satsolvers.pdf

>>>>

Most modern computer systems contain large parts that operate concurrently.
Although the parallelisation of a system can drastically improve its performance, it opens numerous of problems regarding correctness, robustness and reliability, which makes the concurrent program design one of the most difficult problems of programming~\cite{mckenney2017parallel}.
In this work, we consider only \textit{Symmetric Multiprocessor (SMP)} parallelism (systems with multiple processors connected to a single shared memory), leaving aside the discussion on distributed concurrency (systems with autonomous nodes that communicate with each other by passing messages through the network).
%Leaving aside questions on the performance improvement of the system parallelisation, we explore the questions of the \textit{memory consistency},
This thesis discusses mostly the questions on the \textit{memory consistency} rather than performance benefits of the concurrency since inconsistent memory operations can create new program behaviours, unexpected from the programmer's point of view (as well as the loss of expected behaviours), which all can be considered as a security flaw.

@@

The very first tool that performs the WMM-aware portability analysis is \porthos{}%
%
\footnote{The \porthos{} project web site: \url{http://github.com/hernanponcedeleon/Dat3M}} %
%
introduced in April~2017~\cite{Porthos17a}.
This tool reduces described problem to a bounded reachability problem, which can be solved via an SMT-solver (see Section~\ref{ch:enc:bmc}).
This approach allows to capture symbolically the semantics of analysing program and both weak memory models into a single SMT-formula, augmented by the reachability assertion.
As most modern SMT-solvers are efficient enough to be able to operate the state space of size millions of variables bounded by millions of constraints~(\cite{malik2009boolean}), the used method can be applicable in solving the real-world problems.
% about SAT: https://courses.cs.washington.edu/courses/csep573/11wi/lectures/ashish-satsolvers.pdf
